KidsAIR: Main analysis

### 2020-12-11 main_analysis_final.Rmd
update function for interaction analysis

# Run primary model and print results
itt_pm_results_int <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned*int_var + 
                              child_age + 
                       (1 | cohort:area), data = new_model_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emmeans <- emmeans(itt_pm_results_int, pairwise ~ treatment_assigned | int_var)
#summary(int_emmeans, conf.int = TRUE)
save_results <- confint(int_emmeans)
save_results <<- confint(int_emmeans$contrasts)
#save_results

@@

int_function(analysis_data_winter1, "home_sqft_2level")

>>>>

# Run primary model and print results
itt_pm_results_int <<- glmer(log(pm_mean_sampling_period) ~ treatment_assigned*int_var + 
                              child_age + 
                       (1 | cohort:area), data = new_model_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
#summary(itt_pm_results_int)

int_emmeans <- emmeans(itt_pm_results_int, pairwise ~ treatment_assigned | int_var)
#summary(int_emmeans, conf.int = TRUE)
save_contrasts_full <<- summary(int_emmeans)
save_contrasts <<- confint(int_emmeans$contrasts)
obs <<- table(model.frame(itt_pm_results_int)$treatment_assigned)
n_table <<- table(new_model_data$int_var, new_model_data$treatment_assigned)
#save_results

@@

int_function(analysis_data_winter1, "home_sqft_2level")
n_table
save_contrasts
summary_table
save_contrasts_full
